Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife

### 2024-04-03 analysis/paper/paper.Rmd
work on fig 1.

#set paths
data_path_raw <- "analysis/data/raw_data/"
data_path_drvd <- "analysis/data/derived_data/TSA27"

@@

```{r study-area, fig.cap="Road construction costs according to a simple model informed by slope and major barriers (Table 1) in the Revelstoke timber supply area in British Colombia, Canada.", cache=TRUE}
tsaBoundary <- read_sf(here(data_path_raw, "tsa27_boundaries.gpkg"))
#cost surface raster layer
tsaCost <- terra::rast(here(data_path_drvd, "input_cost.tif"))

tsaCost <- terra::mask(tsaCost, terra::vect(tsaBoundary))

@@

tmap_save(tsa, filename = here("analysis/figures/Figure1_StudyArea.png"),
  dpi = 600, insets_tm = canada_overlay, insets_vp = vp,
  height = 6, width = fig_widths["single"], units = "in")

@@

@@

```{r get-data}
# load csv
meanTable <- read.csv(here(data_path_drvd, "mean_table.csv"))
matchData <- read.csv(here(data_path_drvd, "agree_table.csv"))
meanTableRealCuts <- read.csv(here(data_path_drvd,"../TSA27_real_cuts",
                                   "mean_table.csv"))

>>>>

#set paths
data_path_raw <- "analysis/data/raw_data/"
data_path_drvd <- "analysis/data/derived_data/TSA27_real_cuts"

@@

<!---BLOCK_MULTICOL_START--->

```{r prepStudyArea, cache=TRUE}

tsaBoundary <- read_sf(here(data_path_raw, "tsa27_boundaries.gpkg"))
#cost surface raster layer
tsaCost <- terra::rast(here(data_path_drvd, "old cost/input_cost.tif"))
dem <- terra::rast(here(data_path_drvd, "dem/input_cost.tif"))

#tsaCost[tsaCost==65000]=NA
dem[dem==-65000]=NA

tsaCost <- terra::mask(tsaCost, terra::vect(tsaBoundary))
dem <- terra::mask(dem, terra::vect(tsaBoundary))

@@

tmap_save(tsa, filename = here("analysis/figures/Figure1_StudyArea.png"),
  dpi = 600, insets_tm = canada_overlay, insets_vp = vp,
  height = 6*0.9, width = fig_widths["single"]*0.9, units = "in")

tsaDEM <- tm_shape(dem, name = "Elevation")+
  tm_raster(style = "cont", title = "Elevation",palette="Greys")+
  tm_shape(st_union(tsaBoundary))+
  tm_borders(col = "black")+
  tm_compass(position = c(0.3, 0.11), size = 1)+
  tm_scale_bar(position = c("center", "bottom"), text.size = 1)+
  tm_layout(legend.position = c("left", "bottom"),
            legend.bg.color = "white")

tmap_save(tsaDEM, filename = here("analysis/figures/Figure1_StudyAreaDEM.png"),
  dpi = 600, insets_vp = vp,
  height = 6*0.9, width = fig_widths["single"]*0.9, units = "in")

```{r study-area1, fig.cap="Road construction costs according to a simple model informed by slope and major barriers (Table 1) in the Revelstoke timber supply area in British Colombia, Canada."}

@@

```
```{r study-area2}

knitr::include_graphics(here("analysis/figures/Figure1_StudyAreaDEM.png"))
```
<!---BLOCK_MULTICOL_STOP{widths: [3.6,3.6]}--->

```{r study-area, fig.cap="Road construction costs according to a simple model informed by slope and major barriers (Table 1) in the Revelstoke timber supply area in British Colombia, Canada."}

png::writePNG(array(0, dim = c(1,1,4)), here("analysis/figures/empty.png"))
knitr::include_graphics(here("analysis/figures/empty.png"))
```

@@

```{r get-data}
# load csv
meanTable <- read.csv(here(data_path_drvd,"../TSA27", "mean_table.csv"))
matchData <- read.csv(here(data_path_drvd,"../TSA27", "agree_table.csv"))
meanTableRealCuts <- read.csv(here(data_path_drvd,"../TSA27_real_cuts",
                                   "mean_table.csv"))
